The non-random assembly of network motifs in  \nplant-pollinator networks

### 2023-01-13 Manuscript/Main_text/Main_text_Journal_of_Animal_Ecol.Rmd
Minor edit on data availability statement

IB, AA-P and JBL designed the idea. JBL collected the data. AA-P led the analysis with contributions of JBL and guidance of IB. JBL wrote the manuscript with contributions of IB and AA-P.

@@

All data and code are publicly available at Github (<https://github.com/JoseBSL/FunctionalMotifs>) and Zenodo (<https://doi.org/10.5281/zenodo.6489213>).

>>>>

All authors designed the idea. Jose B. Lanuza collected the data. Alfonso Allen-Perkins led the analysis with contributions of Jose B. Lanuza and guidance of Ignasi Bartomeus. Jose B. Lanuza wrote the manuscript with contributions of Ignasi Bartomeus and Alfonso Allen-Perkins.

@@

Data and code available from the online repositories Zenodo  <https://doi.org/10.5281/zenodo.6489213> [@zenodo2022] and Github <https://github.com/JoseBSL/FunctionalMotifs>.
\newpage
